Aircraft Wildlife Collisions

### 2021-07-19 draft_final.Rmd
minor plot changes.

@@

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass, angle=angle) +
  geom_text_wordcloud_area(
    mask = png::readPNG(source="C:/Users/Alex/Documents/flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +#scale_color_continuous("Blues") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )

@@

```{r echo=FALSE, fig.asp=0.5}
#relationship of amount of birds struck with clouds?
birds_strike_sky <- ggplot(birds[!is.na(birds$sky) & !is.na(birds$birds_struck),])+
  aes(x=birds_struck, fill=sky)+
  scale_fill_manual(values = color_pal_sky)+
  geom_bar(position = "fill")+
  labs(title = "Birds struck comparisons",
       subtitle = "Cloudiness by birds struck")

birds_strike_ac_mass <- ggplot(birds[!is.na(birds$ac_mass) & !is.na(birds$birds_struck) & (birds$birds_struck=="0" | as.integer(birds$birds_struck)>3),])+
aes(x=ac_mass, fill=birds_struck)+
  scale_fill_manual(values=c("#eff3ff", "#3182bd", "#08519c")) +
  geom_bar(position = "fill")

@@

```{r echo=FALSE, fig.asp=0.5, warning=FALSE}
above_ground <- birds[as.integer(birds$phase_of_flt)>3 & as.integer(birds$phase_of_flt)<8 & !is.na(birds$phase_of_flt),]
height_by_phase <- ggplot(above_ground) +
  aes(x = phase_of_flt, y = height, fill=phase_of_flt) +
  stat_boxplot(geom="errorbar", width=0.4) +
  scale_fill_brewer(palette="Pastel2") +
  geom_boxplot() +
  coord_flip() +
  theme(axis.title.y = element_blank())+
  labs(title = "Height distribution for flight phases above ground")+
  ylim(0,20000)
# Heights during Descent are on average higher than 
# hypothesis: Collisions happen more often during Descent and are therefore more prominent in the data set?

@@

```{r echo=FALSE, fig.asp=0.5}
#relationship of amount of birds seen with clouds?
birds_seen_plt <- ggplot(birds[!is.na(birds$time_of_day),])+
  aes(x=time_of_day, fill=birds_seen)+
  geom_bar(position = "fill") +
  scale_fill_brewer(palette="BuGn") +
  theme(legend.position="none", axis.title.y = element_blank()) +
  labs(title="Variables influencing birds seen",
       subtitle = "Proportion of birds seen by time of day")

>>>>

#set working dir to where the current file is located
dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
#setwd(dir)

@@

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass, angle=angle) +
  geom_text_wordcloud_area(
    mask = png::readPNG(source="flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +#scale_color_continuous("Blues") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )

@@

```{r echo=FALSE, fig.asp=0.5}
#relationship of amount of birds struck with clouds?
birds_strike_sky <- ggplot(birds[!is.na(birds$sky) & !is.na(birds$birds_struck),])+
  aes(x=birds_struck, fill=sky)+
  scale_fill_manual(values = color_pal_sky)+
  geom_bar(position = "fill")+
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Birds struck comparisons",
       subtitle = "Cloudiness by birds struck")

birds_strike_ac_mass <- ggplot(birds[!is.na(birds$ac_mass) & !is.na(birds$birds_struck) & (birds$birds_struck=="0" | as.integer(birds$birds_struck)>3),])+
aes(x=ac_mass, fill=birds_struck)+
  scale_fill_manual(values=c("#eff3ff", "#3182bd", "#08519c")) +
  geom_bar(position = "fill") + 
  labs(subtitle = "Birds struck subset by aircraft mass")

@@

```{r echo=FALSE, fig.asp=0.5, warning=FALSE}
above_ground <- birds[as.integer(birds$phase_of_flt)>3 & as.integer(birds$phase_of_flt)<8 & !is.na(birds$phase_of_flt),]
height_by_phase <- ggplot(above_ground) +
  aes(x = phase_of_flt, y = height, fill=phase_of_flt) +
  stat_boxplot(geom="errorbar", width=0.4) +
  scale_fill_brewer(palette="Pastel2") +
  geom_boxplot(outlier.size = .9) +
  coord_flip() +
  theme(axis.title.y = element_blank())+
  labs(title = "Height distribution for flight phases above ground")+
  ylim(0,20000)
# Heights during Descent are on average higher than 
# hypothesis: Collisions happen more often during Descent and are therefore more prominent in the data set?

@@

```{r echo=FALSE, fig.asp=0.5}
#relationship of amount of birds seen with clouds?
birds_seen_plt <- ggplot(birds[!is.na(birds$time_of_day),])+
  aes(x=time_of_day, fill=birds_seen)+
  geom_bar(position = "fill") +
  scale_fill_brewer(palette="BuGn") +
  theme(legend.position="none", axis.title.y = element_blank()) +
  labs(title="Variables influencing birds seen",
       subtitle = "Proportion of birds seen by time")
